---
title: "p8105_hw1_xs2635"
author: "Xiaobo Shen"
date: "2026-09-26"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
data("penguins", package = "palmerpenguins")
```

# Problem 1

The important variables are `r names(penguins)`

The penguin species includes `r unique(penguins$species)`.

The islands are `r unique(penguins$island)`.

The recorded sex values are `r unique(penguins$sex)`.

The observation years are `r unique(penguins$year)`

The recorded sex values are `r unique(penguins$sex)`.

This penguins dataset cotains `r nrow(penguins)` observations and `r ncol(penguins)` variables.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)` mm

```{r scatterplot, echo=FALSE, message=FALSE}
ggplot(penguins, aes(x = bill_length_mm,
                     y=flipper_length_mm,
                     color = species)) +
  geom_point(na.rm = TRUE)
ggsave("penguin_scatterpoint.png")
```


# Problem 2
```{r}
x = tibble(
  num_var = rnorm(10),
  log_var = num_var > 0,
  char_var = c("a", "b", "c", "d", "e",
               "f", "g", "h", "i", "j"),
  factor_var = factor(c(
    "level1", "level2", "level3",
    "level1", "level2", "level3",
    "level1", "level2", "level3", "level1"
  ))
)
```
```{r}
mean(pull(x,num_var))
mean(pull(x,log_var))
mean(pull(x,char_var))
mean(pull(x,factor_var))
```
Mean can be calculated for numeric and logical variables, but character and factor variables return NA

```{r, results='hide', warning=FALSE}
as.numeric(pull(x, log_var))
as.numeric(pull(x, char_var))
as.numeric(pull(x, factor_var))
```
True and False in logical variables are converted to 1 and 0, but Character variables return NA because letters cannot be converted to numbers. For the factor variable, their underlying integers can also be converted.
